Prediction maps of defoliation at trees

### 2021-02-07 analysis/report-defoliation.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.retina = 3,
  fig.align = "center",
  out.width = "100%",
  echo = FALSE
)
source(here::here("code/99-packages.R"))
sourceDirectory("R")

@@

  tune_xgboost
)
library("rgdal")
```

@@

```{r}
suppressMessages(getOptPathY(tune_xgboost$opt.path))
```

@@

```{r}
suppressMessages(plotOptPath(tune_xgboost$opt.path))
```

@@

```{r}
hist <- suppressWarnings(suppressMessages(ggplot(defoliation_df_relative[[1]], aes(x = defoliation)) +
  geom_histogram() +
  labs(x = "Relative defoliation of trees") +
  theme_pubr()))
suppressMessages(print(hist))
```

@@

```{r}
hist <- suppressWarnings(suppressMessages(ggplot(defoliation_df_relative[[2]], aes(x = defoliation)) +
  geom_histogram() +
  labs(x = "Relative defoliation of trees") +
  theme_pubr()))
suppressMessages(print(hist))
```

```{r echo = FALSE}
system("rsync -rlptDivzog --chown=*:www-data --chmod=g+r,o+r /home/patrick/papers/2019-feature-selection/docs/figure/report-defoliation.Rmd/defol* patrick@jupiter.geogr.uni-jena.de:/home/www/life-healthy-forest/action-B1-spatial-mapping/defoliation-maps/")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.retina = 3,
  fig.align = "center",
  out.width = "100%",
  echo = FALSE
)
source(here::here("code/99-packages.R"))
load_packages()
sourceDirectory("R")

@@

  tune_xgboost_plan_project
)
```

@@

```{r}
suppressMessages(getOptPathY(tune_xgboost_plan_project$opt.path))
```

@@

```{r}
suppressMessages(plotOptPath(tune_xgboost_plan_project$opt.path))
```

@@

```{r}
hist <- suppressWarnings(suppressMessages(ggplot(
  defoliation_df_relative[[1]],
  aes(x = defoliation)
) +
  geom_histogram() +
  labs(x = "Relative defoliation of trees") +
  theme_pubr()))
suppressMessages(print(hist))
```

@@

```{r}
hist <- suppressWarnings(suppressMessages(ggplot(
  defoliation_df_relative[[2]],
  aes(x = defoliation)
) +
  geom_histogram() +
  labs(x = "Relative defoliation of trees") +
  theme_pubr()))
suppressMessages(print(hist))
```

```{r echo = FALSE}
#system("rsync -rlptDivzog --chown=*:www-data --chmod=g+r,o+r /home/patrick/papers/2019-feature-selection/docs/figure/report-defoliation.Rmd/defol* patrick@jupiter.geogr.uni-jena.de:/home/www/life-healthy-forest/action-B1-spatial-mapping/defoliation-maps/")
```
